Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-03-08 ms.tex
correction from Roc: NEOWISE-Reactivation is a separate project from WISE mission

\begin{abstract} 
Thanks to the Wide-field Infrared Survey Explorer (WISE) mission's
NEOWISE-Reactivation (NEOWISER) program, an entire year of post-reactivation W1
and W2 exposures were made publicly available in 2015. This data set consists of
$\sim$2.5 million exposures in each band, effectively doubling the amount
of WISE imaging available at 3.4$\mu$m and 4.6$\mu$m relative to the AllWISE
release. We have created the first ever full-sky set of coadds combining all 
publicly available W1 and W2 exposures from both the AllWISE and 
NEOWISER mission phases. We employ an adaptation of the unWISE image coaddition
framework \citep{lang14}, which preserves the native WISE angular resolution 
and is optimized for forced photometry. By incorporating two additional scans
of the entire sky, we not only improve the W1/W2 depths, but also largely
eliminate time-dependent artifacts such as off-axis moonlight contamination.
We anticipate that our new coadds will have a broad range of 
applications, including target selection for upcoming spectroscopic cosmology 
surveys, identification of distant/massive galaxy clusters, and discovery
 of high-redshift quasars. In particular, our full-depth 
AllWISE+NEOWISER coadds will be an important input for the Dark Energy 
Spectroscopic Instrument (DESI) selection of luminous red galaxy and quasar 
targets. Our full-depth W1/W2 coadds are already in use within the 
DECam Legacy Survey (DECaLS) and Mayall z-band Legacy Survey (MzLS) reduction 
pipelines. Much more work still remains in order to fully leverage NEOWISER 
imaging for astrophysical applications beyond the solar system.
\end{abstract}

>>>>

\begin{abstract} 
The Near Earth Object Wide-field Infrared Survey Explorer (NEOWISE)
Reactivation mission released data from its first full year of observations
in 2015. This data set includes $\sim$2.5 million exposures in each of W1 and
W2, effectively doubling the amount of WISE imaging available at 3.4$\mu$m and 
4.6$\mu$m relative to the AllWISE release. We have created the first ever 
full-sky set of coadds combining all publicly available W1 and W2 exposures 
from both the AllWISE and NEOWISE-Reactivation (NEOWISER) mission phases. We 
employ an adaptation of the unWISE image coaddition framework \citep{lang14}, 
which preserves the native WISE angular resolution and is optimized for forced 
photometry. By incorporating two additional scans of the entire sky, we not 
only improve the W1/W2 depths, but also largely eliminate time-dependent 
artifacts such as off-axis scattered moonlight. We anticipate that our new 
coadds will have a broad range of applications, including target selection for 
upcoming spectroscopic cosmology surveys, identification of distant/massive 
galaxy clusters, and discovery of high-redshift quasars. In particular, our 
full-depth AllWISE+NEOWISER coadds will be an important input for the Dark 
Energy Spectroscopic Instrument (DESI) selection of luminous red galaxy and 
quasar targets. Our full-depth W1/W2 coadds are already in use within the 
DECam Legacy Survey (DECaLS) and Mayall z-band Legacy Survey (MzLS) reduction 
pipelines. Much more work still remains in order to fully leverage NEOWISER 
imaging for astrophysical applications beyond the solar system.
\end{abstract}
